|

### 2023-04-09 paper.Rmd
fixing spelling in 5.2

In terms of lineups containing heteroskedasticity patterns, `r p_value_cmp_dat %>% filter(type == "heteroskedasticity") %>% count(conv_reject) %>% summarise(pct=round(n[1]/(n[1]+n[2])*100, 0))`% are rejected by conventional tests, while `r p_value_cmp_dat %>% filter(type == "heteroskedasticity") %>% count(reject) %>% summarise(pct=round(n[1]/(n[1]+n[2])*100, 0))`% are rejected by visual tests. When the conventional test rejects a lineup, there is a good chance (`r p_value_cmp_dat %>% filter(type == "heteroskedasticity") %>% filter(conv_reject == "Reject") %>% count(reject) %>% summarise(pct=round(n[1]/(n[1]+n[2])*100, 0))`%) the visual test will also reject it.

>>>>

In terms of lineups containing heteroskedasticity patterns, `r p_value_cmp_dat %>% filter(type == "heteroskedasticity") %>% count(conv_reject) %>% summarise(pct=round(n[1]/(n[1]+n[2])*100, 0))`% are rejected by conventional tests, while `r p_value_cmp_dat %>% filter(type == "heteroskedasticity") %>% count(reject) %>% summarise(pct=round(n[1]/(n[1]+n[2])*100, 0))`% are rejected by visual tests. The visual test rejects `r p_value_cmp_dat %>% filter(type == "heteroskedasticity") %>% filter(conv_reject == "Reject") %>% count(reject) %>% summarise(pct=round(n[1]/(n[1]+n[2])*100, 0))`% of the lineups that the conventional visual test reject.
